---
title: 'svgR in a Markdown Doc'
author: 'author'
date: "2019-06-18"
output: html_document
---

  
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(svgR)
```

## alternatives to append

- get and modify and replace last entry
- get and modify and append last entry

## Bugs and distractions


- saved files appear are now starred on loading,
    - but menu for named shows saveAs , with save greyed out.
- dnds missplaced
    -  selects from current cursor pos to drop pos and replaces all with snippet
- working directory is not the directory to the project
    - getwd() 
    - used to return **"/opt/ptr/resources/library/pointR/App"**
    - now returns **"/home/sup/"** instead of **"/home/sup/AA/diagramMaker"**
    - getDirPath seems to return the path to the project, however, 
      - cannot use inside user-ptr code 
      - cannot set at start up, since we do sourcing there
      - set at each commit?
- CLOSES WINDOW ON *control + x*  (very **BAD**)
- Rmd
    - lacking *xxx* bracing macro (but has  quote macro: "xxx" and {xxx} and (xxx)  )
    - no syntax checks inside code blocks
    - need short cut ctrl+tab to tab line
    - no dnds for R-codeblocks and svgR-code blocks
    - For .Rmd files, canvas should scroll to last edit (but how??)
    - **CRASHES WHEN SELECTION OPEN IN BROWSER** (on laptop)
        -  (but not on desktop machine)
- save on commit option? (or commit on save?)
- lacking zoom for both editor and canvas

## What to create

- text
    - doc title
    - bold
    - big
    - small
- shapes
    - rectangles
        - square corners 
        - rounded corners
    - reactives
        - source (aka value)
        - conductor (aka expression)
        - endpoint (aka observer)
    - data
    - circle
        - empty
        - bullet
    - braces
        - curly
        - square
    - balloons
        - square
        - oval
- arrows
    - sqpuare
    - rounded
    - labeled
- shadows ?


## What is needed in the final diagram product

- add icons for objects 
    - (perhaps just the function, or fn + pmap)
- add icons for arrows
    - (perhaps just the function, or fn + pmap)
- include source files for objects and arrows
    - objects take pointPairs (wh computed internally)
    - arrows take point sequences
- have tibbles to contain objects, 
- have tibbles to contain arrows
- add snapping for objects
- add snapping for arrows
- arrow types
    -  plain
    -  animated 


## rectangles



```{r, results='asis'}
WH=c(300,200)
svgR(
    wh=WH,
    rect(xy=c(50,50),wh=c(200,50), fill='none',stroke='green'),
    rect(xy=c(50,150), wh=c(200,50), fill='none', stroke='red',rx=20)
)
```


## reactive source


###  Using polygon

```{r, results='asis'}
WH=c(300,200)

points<-c(0,0, 100, 0,  150, 50, 100, 100, 0,100)+c(50,50)
svgR(
    wh=WH,
    polygon(points=points, fill='none',stroke='blue', stroke.width=2)
    
)
```

###  Using path


```{r, results='asis'}
WH=c(300,200)

m<-c("M", c(150,50))
polyPortion<-c("l", 100, 0, 50, 50, -50, 50, -100,0)
d=c(m,polyPortion, 'Z')
svgR(
    wh=WH,
   path(d=d, fill='none', stroke='blue', stroke.width=2)
    
)
```

Proposal:  if wh is the bounding box, then the base should be
w-h/2, so we create a fn called reactiveSource as

```{r}
reactiveSource %<c-% function(xy, wh, fill='none', stroke= 'black', ...){
    
    m<-c('M',xy)
    dz<-wh[2]/2
    dx<-wh[1]-dz
    
    polyPortion<-c('l', dx,0,  dz,dz, -dz,dz, -dx, 0 )
    d<-c(m, polyPortion, 'Z')
    
    path(d=d, fill=fill, stroke=stroke, ...)
} 

```


```{r, results='asis'}
WH=c(300,200)
svgR(wh=WH,
 reactiveSource( xy=c(50,50), wh=c(200,50), stroke.width=2)

)

```

### With points arg


```{r}
reactiveSource %<c-% function( points, fill='none', stroke= 'black', ...){
    xy<-apply(points,1,min)
    wh<-abs(apply(points,1,diff))
    m<-c( 'M',points[,1] )
    dz<-wh[2]/2
    dx<-wh[1]-dz
    polyPortion<-c('l', dx,0,  dz,dz, -dz,dz, -dx, 0 )
    d<-c(m, polyPortion, 'Z')
    path(d=d, fill=fill, stroke=stroke, ...)
} 

```


```{r, results='asis'}
WH=c(400,200)
svgR(wh=WH,
 reactiveSource( points=matrix(c(50,50,350,150),2), stroke.width=2, fill='pink')

)

```




## reactive expression

```{r, results='asis'}
WH=c(300,200)

m<-c("M", c(150,50))
polyPortion<-c("l", 100, 0, 50, 50, -50, 50, -100,0)
arcPortion<-c('a', c(50,50), 180, 1,1, c(0,-100))
d=c(m,polyPortion, arcPortion)
svgR(
    wh=WH,
   path(d=d, fill='none', stroke='blue', stroke.width=2)
    
)
```


### reactive expression as a compound


```{r}
reactiveExpression %<c-% function(xy, wh, fill='none', stroke= 'black', ...){
    
   
    dz<-wh[2]/2
    dx<-wh[1]-2*dz
    m<-c('M',xy+c(dz,0))
    polyPortion<-c('l', dx,0,  dz,dz, -dz,dz, -dx, 0 )
    arcPortion<-c('a', c(dz,dz), 180, 1,1, c(0, -2*dz))
    d<-c(m, polyPortion, arcPortion)
    
    path(d=d, fill=fill, stroke=stroke, ... )
} 

```


```{r, results='asis'}
WH<-c(300,200)
svgR(
    reactiveExpression( xy= c(50,50), wh=c(200,50), stroke.width=2)
)

```


### reactive expression as a compound with points arg


```{r}
reactiveExpression %<c-% function(points, fill='none', stroke= 'black', ...){
     xy<-apply(points,1,min)
    wh<-abs(apply(points,1,diff))
   
   
    dz<-wh[2]/2
    dx<-wh[1]-2*dz
    m<-c('M',xy+c(dz,0))
    polyPortion<-c('l', dx,0,  dz,dz, -dz,dz, -dx, 0 )
    arcPortion<-c('a', c(dz,dz), 180, 1,1, c(0, -2*dz))
    d<-c(m, polyPortion, arcPortion)
    
    path(d=d, fill=fill, stroke=stroke, ... )
} 

```


```{r, results='asis'}
WH<-c(300,200)
svgR(
    reactiveExpression( points=matrix(c(50,50,200,150),2), stroke.width=2, fill='orange')
)

```



## reactive observer

```{r, results='asis'}
WH=c(300,200)

m<-c("M", c(150,50))
polyPortion<-c("l", 100, 0, 0, 100,  -100,0)
arcPortion<-c('a', c(50,50), 180, 1,1, c(0,-100))
d=c(m,polyPortion, arcPortion)
svgR(
    wh=WH,
   path(d=d, fill='none', stroke='blue', stroke.width=2)
    
)
```


### reactive observer as a compound


```{r}
reactiveObserver %<c-% function(xy, wh, fill='none', stroke= 'black', ...){
    
   
    dz<-wh[2]/2
    dx<-wh[1]-dz
    m<-c('M',xy+c(dz,0))
    polyPortion<-c('l', dx,0,  0,2*dz, -dx, 0 )
    arcPortion<-c('a', c(dz,dz), 180, 1,1, c(0, -2*dz))
    d<-c(m, polyPortion, arcPortion)
    
    
    path(d=d, fill=fill, stroke=stroke, ... )
} 

```



```{r, results='asis'}
WH<-c(300,200)
svgR(
    reactiveObserver( xy= c(50,50), wh=c(200,50), stroke.width=2)
)

```


### reactive iobserver with points


```{r}
reactiveObserver %<c-% function(points, fill='none', stroke= 'black', ...){
    
    xy<-apply(points,1,min)
    wh<-abs(apply(points,1,diff))
    dz<-wh[2]/2
    dx<-wh[1]-dz
    m<-c('M',xy+c(dz,0))
    polyPortion<-c('l', dx,0,  0,2*dz, -dx, 0 )
    arcPortion<-c('a', c(dz,dz), 180, 1,1, c(0, -2*dz))
    d<-c(m, polyPortion, arcPortion)
    
    
    path(d=d, fill=fill, stroke=stroke, ... )
} 

```



```{r, results='asis'}
WH<-c(300,200)
svgR(
    reactiveObserver( points=matrix(c(50,50,290,150),2), stroke.width=2, fill='yellow')
)

```



## Text

To add text to the above, we can either

1. return a list with object and text
2. return a groub with object and text


## arrows

```{r}
roundedPolyLine%<c-%function(x, r=5, ...){
  nx<-length(x)
  if(nx<4){
    return(NULL)
  }
  n<-ncol(x)
  if(n==2){
    return(path(d=c("M", x[,1], "L", x[,n]), ...))
  }

  dv<-x[,-n]-x[,-1]
  d<-apply( dv ,2, function(x)sqrt(sum(x)^2) )
  lambda<-sapply(r/d, function(x)min(x,.5))
  
  m<- n-1
  if(m==2){
    mA<-matrix(c(lambda[1],1-lambda[1]),2,1)
    mB<-matrix(c(1-lambda[2],lambda[2]),2,1)
  } else {
    mA<- rbind(diag(lambda[-m]),0) + rbind(0,diag(1-lambda[-m]))
    mB<- rbind(0,diag(lambda[-1])) + rbind(diag(1-lambda[-1]),0)
  } 
  a<-x[,-n]%*%mA
  b<-x[,-1]%*%mB   
  rL<-rep("L", n-2)
  rQ<-rep("Q", n-2)
  if(m==2){
    rr<-c(rL,a,rQ,x[,2],b)
  } else {
    rr<-rbind(rL, a, rQ, x[,-c(1,n)], b)
  }
  path(d=c("M", x[,1], rr, "L", x[,n]),  ...)
  }
  ```
  
  ```{r, results='asis'}
  
  WH<-c(500,300)
  svgR(
  wh=WH,
  roundedPolyLine(
    x=matrix(c(100,100,100,200,300,200),2),
    r=10, 
    fill='none',
    stroke='red',
    marker.end=
        marker( viewBox=c(0, 0, 10, 10), refXY=c(9,5), 
              markerWidth=6, markerHeight=6, orient="auto",
              path( d=c("M", 0, 0, "L", 10, 5, "L", 0, 10, "z") )
       
        )
        )
  )
  ```
  
  ### alternatively including marker in arrow def
  
  
  ```{r}
arrow %<c-% function(x, r=5, ...){
  nx<-length(x)
  if(nx<4){
    return(NULL)
  }
  n<-ncol(x)
  if(n==2){
    return(path(d=c("M", x[,1], "L", x[,n]), ...))
  }

  dv<-x[,-n]-x[,-1]
  d<-apply( dv ,2, function(x)sqrt(sum(x)^2) )
  lambda<-sapply(r/d, function(x)min(x,.5))
  
  m<- n-1
  if(m==2){
    mA<-matrix(c(lambda[1],1-lambda[1]),2,1)
    mB<-matrix(c(1-lambda[2],lambda[2]),2,1)
  } else {
    mA<- rbind(diag(lambda[-m]),0) + rbind(0,diag(1-lambda[-m]))
    mB<- rbind(0,diag(lambda[-1])) + rbind(diag(1-lambda[-1]),0)
  } 
  a<-x[,-n]%*%mA
  b<-x[,-1]%*%mB   
  rL<-rep("L", n-2)
  rQ<-rep("Q", n-2)
  if(m==2){
    rr<-c(rL,a,rQ,x[,2],b)
  } else {
    rr<-rbind(rL, a, rQ, x[,-c(1,n)], b)
  }
 
    path(
        d=c("M", x[,1], rr, "L", x[,n]),  
        fill='none',
        marker.end= marker( viewBox=c(0, 0, 10, 10), refXY=c(9,5), 
              markerWidth=6, markerHeight=6, orient="auto",
              path( d=c("M", 0, 0, "L", 10, 5, "L", 0, 10, "z") )
       
        ),
    ...)
 
  }
  ```
  
  ```{r, results='asis'}
  
  WH<-c(500,300)
  svgR(
  wh=WH,
  arrow(
    x=matrix(c(100,100,100,200,300,200),2)
   
    )
  )
  ```

