---
title: 'svgR in a Markdown Doc'
author: 'author'
date: "2020-02-04"
output: html_document
---

  
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(svgR)
```


# Steps to Implement *shinyInputControl*

In what follows steps 1-3 address server to client, steps 4-6 address client to server. Step 7 involves client to server back to client.

### 1. Building your svg

```{r, results='asis' }
box %<c-% function(pos, i, headTxt, fill, valTxt, valTxt2=NULL, valTxt3=NULL ){
    g(
         rect(
               xy=pos$rectXY[,i],
               wh=pos$rectWH[,i],
               fill=fill,
               stroke='blue',
               stroke.width=3
             ), 
             text(headTxt,
                xy=pos$headXY[,i],
                stroke='blue' 
             ),
             text(valTxt,
                xy=pos$txt1XY[,i]
             ),
             if(!is.null(valTxt2)){
                text(valTxt2,
                xy=pos$txt2XY[,i]
             ) 
             } else {
                 NULL
             },
             if(!is.null(valTxt3)){
                text(valTxt3,
                xy=pos$txt3XY[,i]
             ) 
             } else {
                 NULL
             }
    )
}

dimInit<-function(rectH){
  sep<-5
  rectW<-250
  rectY<-cumsum(c(0,rectH)+sep)
  rectXY<-rbind(100,rectY)
  rectWH<-rbind(250,rectH)
  headXY<-c(10,20)+rectXY
  txt1XY<-c(30,20)+headXY
  txt2XY<-c(0,20)+txt1XY
  txt3XY<-c(0,20)+txt2XY
  WH<-c(400,sum(rectH)+(1+length(rectH))*sep)
  list(
    rectXY=rectXY,
    rectWH=rectWH,
    headXY=headXY,
    txt1XY=txt1XY,
    txt2XY=txt2XY,
    txt3XY=txt3XY,
    WH=WH
  )
}

rectH<-c(90,50)
pos<-dimInit(rectH)
WH<-pos$WH

WH<-c(400,200)
svgR(wh=WH,text('STEP 1',xy=c(20,20)),
    box(pos, 1, 'shinyInputControl_svg.R', '#BBFFBB','add to parms', 'edit svgR','commit svg'),
    box(pos, 2, 'app.R', '#FFCCAA','run to test')

 
)
```

1. In file **shinyInputControl_svg.R** 
    1. Add to Parameters section as needed
        - Parameters section contains variables:
            - WH (width height) 
            - ID for the contol id
            - CMDS (may supply more than one)
        - Add here anything you want to be adjustable
    2. add to the svgR(){} what you want to see
    3. commit to test image
2. run to test App 
 

### 2. Initializing the Control

```{r, results='asis' }

rectH<-c(50,70,70,50)
pos<-dimInit(rectH)
WH<-pos$WH


svgR(wh=WH, text('STEP 2',xy=c(20,20)),
    box(pos, 1, 'app.R', 'pink','edit intialValue'),
    box(pos, 2, 'shinyInputControl.R', 'lightyellow','edit shinyInputControl()'),
    box(pos, 3, 'shinyInputControl.js', 'lightblue','edit shinyInputControl()'),
    box(pos, 4, 'app.R', '#FFCCAA','run to test')
     
)
```

1. In file **app.R**
   1. set **initialValue** as appropriate
   2. edit *ui*  if needed
   3. edit *server* if needed
2. In file **shinyInputControl.R** 
    - in function *shinyInputControl()*
        -  if necessary (*when value not a string*)
            1. preprocess the *value* argument 
            2. edit params 
            3. edit 'data-value'=value
        - **note:** we can have more than one value
3. In file **shinyInputControl.js**
    - if necessary  (*when value is to be object*)
        - in function **initialize**
            1. extract value from data-value attribute
               - Hint use:
``` {r, results='asis'}
library(svgR)
WH<-c(48,32)
R<-.06*WH[1]
d<-list(M=WH*c(.65,.2), Q=WH*c(c(.25,.15),c(.25,.4)))
R<-.06*WH[1]
svgR(wh=WH, 
  rect( xy=c(0,0), wh=WH, fill='black'), 
  path(d=d, stroke="#00FFFF", stroke.width=2,
        marker.end=marker(viewBox=c(0, 0, 10, 10), 
        refXY=c(1,5), stroke.width=1, fill="#00FFFF",
        markerWidth=4, markerHeight=5, orient="auto",
        path( d=c("M", 0, 0, "L", 9, 5, "L", 0, 9, "z") )
    ) ),
  text(xy=WH*c(.05,.9),'attr', fill="#00FFFF"),
  text(xy=WH*c(.7,.4),'el', fill="#00FFFF")
)
```
            2. do any needed processing of value
                - for example, *if a value represents an object*, then convert to object
                    - Hint use:
```{r, results='asis'}
library(svgR)
WH<-c(48,32)
ptR<-list(
  x=matrix(0,2,0)
)
r=WH[2]/3
lft=WH[1]/2-1.5*r
top<-WH[2]/2-r
bot<-WH[2]/2+r
svgR(wh=WH, 
  rect( xy=c(0,0), wh=WH, fill='black'), 
  polygon(points=WH*c(c(.05,.5), c(.15,.3),c(.15,.7)),fill='#00FFFF'),
  rect(cxy=WH*c(.2,.5), wh=WH*c(.1,.1),fill="#00FFFF"),
  circle(
    cxy=WH/2,
    r=WH[2]/3,
    stroke='none',
    fill='#00FFFF'
  ),
  path(
    d=list(
      M=c(.4,.8)*WH, 
      C=c( c(.6,1.2),c(.9,.2), c(.8,.9))*WH
    ),
    stroke='#00FFFF',
    stroke.width=1,
    fill='none'
  ),
  g(
      lapply(1:3, function(i){
        ellipse(cxy=WH*c(.5, .1), rxy=i*c(8,3), fill='none', stroke='#000000', stroke.width=.5)
      }),
      mask=mask(circle(cxy=WH/2, r=WH[2]/3), fill='white' )
  ),
  g(
    lapply(1:5, function(i){
      ellipse(cxy=WH*c(.7, .5), rxy=i*c(3,5), fill='none', stroke='#000000', stroke.width=.5)
    }), 
    mask=mask(
      circle(cxy=WH/2, r=WH[2]/3, fill='white'),
      ellipse(cxy=WH*c(.5, .1), rxy=3*c(8,3), fill='black')
    )
  ),
   g(
    lapply(1:5, function(i){
      ellipse(cxy=WH*c(.3, .3), rxy=i*c(3,5), fill='none', stroke='#000000', stroke.width=.5)
    }), 
    mask=mask(
      circle(cxy=WH/2, r=WH[2]/3, fill='white'),
      ellipse(cxy=WH*c(.5, .1), rxy=3*c(8,3), fill='black'),
      ellipse(cxy=WH*c(.7, .5), rxy=5*c(3,5), fill='black')
    )
  )
)
```                  
            3. set data-value 
               - Hint use: 
```{r, results='asis'}
library(svgR)
WH<-c(48,32)
R<-.06*WH[1]
d<-list(M=WH*c(.8,.85), Q=WH*c(c(.12,.85),c(.12,.52)))

svgR(wh=WH, #stroke.width=1, stroke="#00FFFF",  fill="none",
  rect( xy=c(0,0), wh=WH, fill='black'), 
  polygon(points=WH*c(c(.25,.5), c(.15,.3),c(.15,.7)),fill='#00FFFF'),
  rect(cxy=WH*c(.1,.5), wh=WH*c(.1,.1),fill="#00FFFF"),
   lapply(1:5, function(i){
       ellipse(
       cxy=c(.6, .8-i*.1)*WH,
       rxy=c(.2,.1)*WH,
       stroke='black',
       fill='#00FFFF',
       stroke='black',
       stroke.width=.5
      )
     })
)
```
    - if value is a character string, nothing need be done
4. run **App.R** and use browser to verify *data-value* attached
    - in the browser panel (right hand side) 
        - locate the div with the id matching your control id 
        - verify that the *data-value* attribute appears and has the value you assigned

### 3. Implementing  Update using a Braindead Approach

```{r, results='asis'}
rectH<-c(70,90,90,50)
pos<-dimInit(rectH)
WH<-pos$WH


svgR(wh=WH, text('STEP 3',xy=c(20,20)),
    box(pos, 1, 'app.R', 'pink','edit observer for update'),
    box(pos, 2, 'shinyInputControl.R', 'lightyellow','recreate svgTree', 'create & send message'),
    box(pos, 3, 'shinyInputControl.js', 'lightblue','extract value and set element', 'extract and replace tree'),
    box(pos, 4, 'app.R', '#FFCCAA','run to test')
)
```


1. In **App.R** 
    - Edit *observeEvent(input\$updateButton* to call
       - *updateshinyInputControl* with a proper value
2. In file **shinyInputControl.R** 
  - In the function **updateShinyInputControl**
    1. Recreate svg Tree (), 
        - this will entail creating the following
            - params=list(ID=inputId, WH=wh, value=value) 
            - svgTree<-*shinyInputControlWrapper*(params=params)
            - node<-as.character(svgTree)
        - may be necessary to edit params=list
    2. Form a message to send to the client
          - mssg<-list( value=value, node=node) 
    3. Send the message to client
          - session\$sendInputMessage(inputId, mssg)
  - Hint: 
```{r, results='asis' }
  library(svgR)
WH<-c(48,32)
X=c(.2,.4,.6,.8)

svgR(wh=WH, stroke.width=3, stroke="#00FFFF",  fill="#00FFFF",
  rect( xy=c(0,0), wh=WH, fill='black'), 
  line(xy1=WH*c(.1,.1), xy2=WH*c(.9,.1)   ),
  line(xy1=WH*c(.1,.23), xy2=WH*c(.9,.23) ),
  line(xy1=WH*c(.5,.4), xy2=WH*c(.5,.9) ),
  polygon(points=WH*c( .5,.3, .7,.5, .3,.5))

)
```
3. In file **shinyInputControl.js** in function *receivemessage*
    1. extract value(s) 
        - var value = data.value;
        - Hint use: 
```{r, results='asis'}
library(svgR)
WH<-c(48,32)
svgR(wh=WH, 
     rect(xy=c(0,0), wh=WH, fill='black'),
  text(cxy=WH/2, "Xval", stroke='#00FFFF', fill='#00FFFF')
)
```
    2. If needed, convert to object: i.e. value=JSON.parse(value);
      - Hint use: 
```{r, results='asis'}
library(svgR)
WH<-c(48,32)
r=WH[2]/3
lft=WH[1]/2-1.5*r
top<-WH[2]/2-r
bot<-WH[2]/2+r
svgR(wh=WH, rect(xy=c(0,0),wh=WH, fill='black'),
  polygon(points=WH*c(c(.05,.5), c(.15,.3),c(.15,.7)),fill='#00FFFF'),
  rect(cxy=WH*c(.2,.5), wh=WH*c(.1,.1),fill="#00FFFF"),
  circle(
    cxy=WH/2,
    r=WH[2]/3,
    stroke='none',
    fill='#00FFFF'
  ),
  path(
    d=list(
      M=c(.4,.8)*WH, 
      C=c( c(.6,1.2),c(.9,.2), c(.8,.9))*WH
    ),
    stroke='#00FFFF',
    stroke.width=1,
    fill='none'
  ),
  g(
      lapply(1:3, function(i){
        ellipse(cxy=WH*c(.5, .1), rxy=i*c(8,3), fill='none', stroke='#000000', stroke.width=.5)
      }),
      mask=mask(circle(cxy=WH/2, r=WH[2]/3), fill='white' )
  ),
  g(
    lapply(1:5, function(i){
      ellipse(cxy=WH*c(.7, .5), rxy=i*c(3,5), fill='none', stroke='#000000', stroke.width=.5)
    }), 
    mask=mask(
      circle(cxy=WH/2, r=WH[2]/3, fill='white'),
      ellipse(cxy=WH*c(.5, .1), rxy=3*c(8,3), fill='black')
    )
  ),
   g(
    lapply(1:5, function(i){
      ellipse(cxy=WH*c(.3, .3), rxy=i*c(3,5), fill='none', stroke='#000000', stroke.width=.5)
    }), 
    mask=mask(
      circle(cxy=WH/2, r=WH[2]/3, fill='white'),
      ellipse(cxy=WH*c(.5, .1), rxy=3*c(8,3), fill='black'),
      ellipse(cxy=WH*c(.7, .5), rxy=5*c(3,5), fill='black')
    )
  )
)
```
    3. set element with new data
        - this.setValue(\$(el), value);
        - Hint use:
```{r, results='asis'}
library(svgR)
WH<-c(48,32)
svgR(wh=WH, rect(xy=c(0,0), wh=WH, fill='black'),
  text(cxy=WH/2, "Sval", stroke='#00FFFF', fill='#00FFFF')
)
```
    4. update svg rendering by replacing the entire svgTree under the $(el)
        - let node=data.node; 
        - \$(el).empty().append(node); //this replaces the svgTree
        - Hint use:
``` {r, results='asis'}
library(svgR)
WH<-c(48,32)
R<-.06*WH[1]
d<-list(M=WH*c(.2,.42), Q=WH*c(c(.2,.8),c(.5,.8)))

svgR(wh=WH, stroke.width=2, stroke="#00FFFF",  fill="none",
     rect(xy=c(0,0), wh=WH, fill='black'),
    text(xy=WH*c(.16,.38),'svg', stroke.width=1, fill="#00FFFF"),
    ellipse(cxy=WH*(c(1,1)-c(.2,.55)),  rxy=R*c(2,1), fill="#00FFFF"),
    line(xy1=WH*(c(1,1)-c(.2,.1)), xy2=WH*(c(1,1)-c(.2,.3)) ),
    line(xy1=WH*(c(1,1)-c(.2,.3)), xy2=WH*(c(1,1)-c(.25,.5)),stroke.width=1.5 ),
    line(xy1=WH*(c(1,1)-c(.2,.3)), xy2=WH*(c(1,1)-c(.15,.5)),stroke.width=1.9 ),
    path(d=d, stroke="#00FFFF", 
        marker.end=marker(viewBox=c(0, 0, 10, 10), refXY=c(1,5), stroke.width=1, fill="#00FFFF",
        markerWidth=4, markerHeight=5, orient="auto",
        path( d=c("M", 0, 0, "L", 9, 5, "L", 0, 9, "z") )
    ) 
    )
)
```
4. In **App.R** validate that *updateshinyInputControl* works:
        -  the appearance changes
        -  value changes



### 4. Adding mouse events

```{r, results='asis'}
rectH<-c(70,50)
pos<-dimInit(rectH)
WH<-pos$WH

svgR(wh=WH,text('STEP 4',xy=c(20,20)),
    box(pos, 1, 'shinyInputControl_svg.R', '#BBFFBB','add mouse events'),
    box(pos, 2, 'app.R', '#FFCCAA','run to test')
)
```

- In file **shinyInputControl_svg.R** 
    - add *onclick=CMDS*  for interactivity
    - Hint use:
```{r, results='asis'}
 
library(svgR)
WH<-c(48,32)
R<-WH[1]*.2
CXY=WH*c(.3,.5)
svgR(wh=WH,  stroke="#00FFFF",  fill="none",
    rect(xy=c(0,0), wh=WH, fill='black'),
    g(
        polygon(
            points=c(WH)*c(
                c(.0,.0),c(.2,.5), c(.05,.3), c(.05,.6),
                c(-.05,.6),c(-.05,.3), c(-.2,.5)
            ),
            stroke="#00FFFF"
        ),
        lapply(c(0,45,135,180), function(theta){
            line(xy1=c(.1,0)*WH, xy2=c(.3,0)*WH, stroke="#00FFFF",
            transform=list(rotate=-theta)
            )
        }),
        transform=list( translate=WH*c(.6,.45), rotate=65)
    )
)
```

- run **App.R** and test for on an click message
- use browser to verify value was assigned 


### 5. Adding Mouseclick Handler

```{r, results='asis' }
rectH<-c(70,70,50)
pos<-dimInit(rectH)
WH<-pos$WH

svgR(wh=WH,text('STEP 5',xy=c(20,20)),
    box(pos, 1, 'shinyInputControl.js', 'lightblue','add clicked:'),
    box(pos, 2, 'shinyInputControl.R', 'lightyellow','edit params$CMDS'),
    box(pos, 3, 'app.R', '#FFCCAA','run to test')
)
```

1. In **shinyInputControl.js**
    - add handler **clicked:** (assuming you are using mouse click)
        - Hint use:
``` {r, results='asis'}
library(svgR)
WH<-c(48,32)
R<-WH[1]*.2
CXY=WH*c(.3,.5)
svgR(wh=WH,  stroke="#00FFFF",  fill="none",
     rect(xy=c(0,0), wh=WH, fill='black'),
    circle(cxy=CXY+c(-R,-R), r=R/4,  fill='#00FFFF'),
    circle(cxy=CXY+c(-R,+R), r=R/4,  fill='#00FFFF'),
    g(
        polygon(
            points=c(WH)*c(
                c(.0,.0),c(.2,.5), c(.05,.3), c(.05,.6),
                c(-.05,.6),c(-.05,.3), c(-.2,.5)
            ),
            stroke="#00FFFF"
        ),
        lapply(c(0,45,135,180), function(theta){
            line(xy1=c(.1,0)*WH, xy2=c(.3,0)*WH, stroke="#00FFFF",
            transform=list(rotate=-theta)
            )
        }),
        transform=list( translate=WH*c(.6,.45), rotate=65)
    )
)
```
        - typically this will
            - if needed: 
                - convert id to el (el='#'+id)
            - make a call to **this.getValue(el)**
            - do something
            - make a call to **this.setValue(el, value)**
                - Hint use:
```{r results='asis'}
library(svgR)
WH<-c(48,32)
svgR(wh=WH, rect(xy=c(0,0), wh=WH, fill='black'),
  text(cxy=WH/2, "Sval", stroke='#00FFFF', fill='#00FFFF')
)
```
2. In **shinyInputControl.R**
    - edit **params\$CMDS** to use cmd in client. 
        - for example to handle a mouse click, add 
          - sprintf('shinyInputControlBinding.clicked("%s", "%s", evt)',params\$ID, mssg)
          - where mssg contains some additional info
          - Hint use: 
```{r, results='asis' }
library(svgR)
WH<-c(48,32)
ptR<-list(
  x=matrix(0,2,0)
)
R<-WH[1]*.2
CXY=WH*c(.3,.5)
svgR(wh=WH,  stroke="#00FFFF",  fill="none",
     rect(xy=c(0,0), wh=WH, fill='black'),
    text(xy=c(.05,.3)*WH,'CMDS', font.size=9),
    g( 
        polygon(
            points=c(WH)*c(
                c(.0,.0),c(.2,.5), c(.05,.3), c(.05,.6),
                c(-.05,.6),c(-.05,.3), c(-.2,.5)
            ),
            stroke="#00FFFF"
        ),
        lapply(c(0,45,135), function(theta){
            line(xy1=c(.1,0)*WH, xy2=c(.3,0)*WH, stroke="#00FFFF",
            transform=list(rotate=-theta)
            )
        }),
        transform=list( translate=WH*c(.6,.45), rotate=65)
    )
)
```
3. run **App.R** and use browser to verify data-value is modified on click

### 6. Handling Return Values From Client

```{r, results='asis' }

rectH<-c(70,50)
pos<-dimInit(rectH)
WH<-pos$WH

svgR(wh=WH,text('STEP 6',xy=c(20,20)),
    box(pos, 1, 'shinyInputControl.R', 'lightyellow','registerInputHandler'),
    box(pos, 2, 'app.R', '#FFCCAA','run to test')
)
```

1. In file **shinyInputControl.R** 
    - in *registerInputHandler*
        - do any post processing of value and return value
2. test return value of input\$controlId in App.R


### 7. Updating the Appearance Upon Receiving Input 

```{r, results='asis' }
rectH<-c(70,50)
pos<-dimInit(rectH)
WH<-pos$WH

svgR(wh=WH,text('STEP 7',xy=c(20,20)),
    box(pos, 1, 'shinyInputControl.R', 'lightyellow','add to registerInputHandler', 'updateshinyInputControl(...)'),
    box(pos, 2, 'app.R', '#FFCCAA','run to test')
)

```



- In **shinyInputControl.R**
    - In *registerInputHandler* prior to returning value
        - add *updateshinyInputControl(...)* 
        - Hint use: 
```{r, results='asis',}
library(svgR) 
WH<-c(48,32)
ptR<-list(
  x=matrix(0,2,0)
)


svgR(wh=WH, stroke.width=3, stroke="#00FFFF",  fill="#00FFFF",
  rect(xy=c(0,0), wh=WH, fill='black'),
  line(xy1=WH*c(.1,.1), xy2=WH*c(.9,.1) ),
  line(xy1=WH*c(.1,.23), xy2=WH*c(.9,.23) ),
  polygon(points=WH*c( .5,.3, .7,.5, .3,.5)),
  polyline(points=WH*c(.1, .5, .1,.85, .5,.85, .5,.4 ) , fill="none")
)
```      


